%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[]{mcdowellcv}

% For mathematical symbols
\usepackage{amsmath}

% Set applicant's personal data for header
\name{Ahmed Bahnasy}
\address{Paul-Hindemith-Allee 4, 213 \linebreak Munich 80939}
\contacts{(+49) 163-524-1460 \linebreak asbahnasy@gmail.com}

\begin{document}

	% Print the header
	\makeheader
	
	% Print the content
	\begin{cvsection}{Education}
		\begin{cvsubsection}{Munich, Germany}{Technische Universit채t M체nchen}{Fall 2019 -- Present}
			\begin{itemize}
				\item MS.c. in Informatics, Focus on Machine Learning and Computer vision
				\item Selected Coursework: Multiple View Geometry, Tracking and Detection in Computer Vision, Advanced Deep Learning in Computer Vision, Machine Learning in Computer Vision
			\end{itemize}
		\end{cvsubsection}
		\begin{cvsubsection}{Cairo, Egypt}{The German University in Cairo}{Fall 2011 -- Fall 2016}
			\begin{itemize}
				\item BS.c. in Mechatronics Engineering. GPA: 2.0.
				\item Thesis Grade: 1.0
				\item Semester abroad at Berlin Campus. Sept 2014 -- Jan 2015
%				\item Selected Coursework: Image processing, Visual Servoing, Autonomous systems, Data Structures \& Algorithms, Numerical Analysis, Classical and Modern Control.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Employment}
	\begin{cvsubsection}{Master Thesis Student}{Helmholtz Zentrum M체nchen}{Feb. 2022 - Jul. 2022}
			Computer Vision - Institute of Computational Biology		
			\begin{itemize}	
			\item Thesis Title: Optimization of instance segmentation performance for fragmented and strong occlusions in neonatal incubator environments
			\end{itemize}
		\end{cvsubsection}
		\begin{cvsubsection}{Working Student}{ESR Labs, Accenture}{Apr. 2021 - Feb. 2022}
			Computer Vision - Machine Learning Team			
			\begin{itemize}
				\item Work on deep learning algorithms for camera centric automotive perception (Monocular Depth Estimation and Segmentation Tasks)
				\item Support in training, evaluating and optimizing inference time of DL models 
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Student Researcher}{Visual Computing Lab - TUM}{Nov. 2020 -  Apr. 2021}
			Guided Research Project
			\begin{itemize}
				\item working on 3D object detection and Tracking using Graph Neural Networks for Autonomous Driving
			\end{itemize}
		\end{cvsubsection}

		
		\begin{cvsubsection}{Working Student}{Allianz SE}{Jan. 2020 -  Aug. 2020}
			Data Science Team - Group Data Analytics
			\begin{itemize}
				\item Developing AI solutions that enhance and improve customer experience
				\item support in developing statistical learning models for data analysis
				\item support in preparing and communicating results to decision makers
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Software Engineer, Full-time}{Valeo, Automotive}{Apr. 2017 -- Sept. 2019}	
			%Integrator, SW Platform Team (Dec. 2018 -- Sept. 2019)
			\begin{itemize}
				\item Integrating SW Platform AUTOSAR compliant SW components across different projects.
				\item developed integration and testing environment using CANoe, CAPL scripting that reduced test release time by more than 80\%.
				\item Projects involved; Peugeot S.A. Front Camera,Climate Control, headlights and steering ECUs.
			%\end{itemize}
			%Developer, SW Platform Team (Feb. 2018 -- Dec. 2018)
			%\begin{itemize}
				\item developing standardized, AUTOSAR and MISRA-C compliant SW components for ECUs diagnostics and mode management functions
				\item Requirement analysis, functional specification, implementation, and testing of software functions.
			\end{itemize}
			%Linux Developer, SW Innovation Team (Apr. 2017 -- Feb. 2018)
			%\begin{itemize}
			%	\item benchmarking, developing and prototyping new trends in automotive industry 
			%	\item Projects involved: AUTOSAR over Linux Demo, Developing AUTOSAR MCAL wrapper Layer for Integrity OS.
			%\end{itemize}
			
		\end{cvsubsection}
		
		\begin{cvsubsection}{Control Engineer, Full-time}{Advansys, ESC.}{Sept. 2016 -- Apr. 2017}
			Emulation team
			\begin{itemize}
				\item Design / run test scenarios for PLC control software.
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Research Intern}{Hochschule f체r Technik und Wirtschaft, Berlin}{Jul 2015 -- Aug 2015}
			Control and Dynamics Lab		
			\begin{itemize}
				\item Developed a digital control system for ball magnetic levitation system.
			\end{itemize}
		\end{cvsubsection}
		
	\end{cvsection}
	
	\begin{cvsection}{Technical Experience}
		\begin{cvsubsection}{Projects}{}{}
			\begin{itemize}
				\item \textbf{Monocular Depth Estimation for Autonomous Driving} (2021). \textit{Pytorch}
					\begin{itemize}
						\item self-supervised approach to overcome the challenge of per-pixel ground-truth depth data acquisition at scale.
					\end{itemize}
				\item \textbf{2D Object Tracking using Graph Neural Networks} (2021). \textit{Pytorch}
					\begin{itemize}
						\item Pedestrian Tracking using GNNs
						\item Benchmarking on the public dataset "MOT Challenge dataset".
					\end{itemize}
				\item \textbf{Point Cloud Segmentation using Graph Neural Networks} (2020). \textit{Pytorch}
					\begin{itemize}
						\item using only few semantic labels, use GNN to propagate the known labels to nodes with unknown labels.
					\end{itemize}
				\item \textbf{3D Object Detection on Waymo Lidar dataset using Point Features} (2020). \textit{Pytorch}
					\begin{itemize}
						\item Using Anchor free approach to detect bounding boxes as key point features
					\end{itemize}
				\item \textbf{3D pose estimation and object instance recognition} (2019). \textit{Pytorch, Scikit-learn, pandas, python}
				\item \textbf{Object Classification, and detection using HOG features and Random forests} (2019). \textit{OpenCV, C++}
%				\item \textbf{AUTOSAR over Linux} (2017). running autosar over embedded Linux image. \textit{Yocto, Embedded Linux, C++, Cmake}
			\end{itemize}
		\end{cvsubsection}
		\begin{cvsubsection}{Open Source Contributions}{}{}		
		\begin{itemize}
						\item \textbf{BlenderProc} (2020). \textit{Python}
				\begin{itemize}
					\item Open source project maintained by German Aerospace Center (DLR) - Institute of Robotics and Mechatronics (RM)
					\item Blender Proc is a procedural Blender pipeline for photorealistic training image generation.
					\item implemented the first data loader that loads human poses models into scene to render human pose training images.
					\item The data loader handles AMASS Dataset, a large database of human motion.
				\end{itemize}
\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	%\begin{cvsection}{Publications}
	%	\begin{cvsubsection}{}{}{}
	%		\textbf{Rescue Missions Bots using Active SLAM and Map Feature Extraction}
	%		\begin{itemize}
	%			\item 2016 | International Conference on Control, Mechatronics and Automation.
	%			\item Authors: M Nabil,  M. H. Kassem, A Bahnasy, Omar M. Shehata, El-Sayed I. Morgan
	%		\end{itemize}
	%	\end{cvsubsection}
	%\end{cvsection}
	
	\begin{cvsection}{Languages and Technologies}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item Languages: C++, Python
				\item Tools/Frameworks/Libraries: PyTorch, Git, Linux
				\item Infrastructure: SLURM, GCP, AWS
				\item Automotive Technologies: AUTOSAR, CANoe, CAPL Scripting
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}


	%\begin{cvsection}{Extra-Curricular Activities}
	%	\begin{cvsubsection}{Volunteering}{}{}	
	%		
	%		\begin{itemize}
	%			\item Dive In TEDxTUM Event | Operations Volunteer | Munich, Nov. 2019
	%			\item Coral Reefs Cleaning campaign | SCUBA Diver Volunteer | Nuweiba, RedSea, Egypt | Mar. 2019
	%			\item Cairo Runners Cairo Half Marathon 2016 | Operations Volunteer | Cairo, Apr. 2016
	%			\item Alashanek Ya Balady for Sustainable Development, NGO | Operations Volunteer  Nov. 2013 -- Jun. 2016
	%		\end{itemize}
	%	\end{cvsubsection}
	%\end{cvsection}

	
	
\end{document}
